---
title: "Homework 6"
author: "Juyoung Hahm"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

```{r load_libraries}
library(tidyverse)
library(modelr)
library(p8105.datasets)
```

# Problem 1

```{r}
homicide_df = 
  read_csv("homicide-data.csv", na = c("", "NA", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1)
  ) %>% 
  filter(
    victim_race %in% c("White", "Black"),
    city_state != "Tulsa, AL") %>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)
```


Start with one city.

```{r}
baltimore_df =
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")
glm(resolution ~ victim_age + victim_race + victim_sex, 
    data = baltimore_df,
    family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digits = 3)
```


Try this across cities.

```{r}
models_results_df = 
  homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = 
      map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)
  ) %>% 
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state, term, OR, starts_with("CI")) 
```

```{r}
models_results_df %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```



# Problem 2

Find some residuals

```{r}
baby_df = 
  read_csv("./birthweight.csv")
```

Load and clean the data for regression analysis (i.e. convert numeric to factor where appropriate, check for missing data, etc.).
```{r}
baby_df$babysex=as.factor(baby_df$babysex)
baby_df$frace=as.factor(baby_df$frace)
baby_df$malform=as.factor(baby_df$malform)
baby_df$mrace=as.factor(baby_df$mrace)

sum(is.na(baby_df))

```

propose linear regression model for `birthweight`
```{r}
bweight_lm = lm(bwt ~ blength + gaweeks + momage, data = baby_df)
summary(bweight_lm)

```
plot of model residuals against fitted values
Describe your modeling process and show a plot of model residuals against fitted values – use add_predictions and add_residuals in making this plot.
```{r}
modelr::add_residuals(baby_df, bweight_lm)
modelr::add_predictions(baby_df, bweight_lm)

baby_df %>%
  add_residuals(bweight_lm) %>%
  add_predictions(bweight_lm) %>%
  add_residuals(smooth_mod, var = "resid_loess") %>%
  add_predictions(smooth_mod, var = "pred_loess")

baby_df %>% 
  modelr::add_residuals(bweight_lm) %>% 
  ggplot(aes(x = blength, y = resid)) + geom_point()

baby_df %>% 
  modelr::add_residuals(bweight_lm) %>% 
  ggplot(aes(x = gaweeks, y = resid)) + geom_point()

baby_df %>% 
  modelr::add_residuals(bweight_lm) %>% 
  ggplot(aes(x = momage, y = resid)) + geom_point()


```

```{r}
smooth_mod = mgcv::gam(bwt ~ s(gaweeks), data = baby_df)
linear_mod = lm(bwt ~ gaweeks, data = baby_df)
wiggly_mod = mgcv::gam(bwt ~ s(gaweeks, k = 30), sp = 10e-6, data = baby_df)

baby_df %>% 
  gather_predictions(linear_mod, smooth_mod, wiggly_mod) %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = gaweeks, y = bwt)) + 
  geom_point() + 
  geom_line(aes(y = pred), color = "red") + 
  facet_wrap(~model)
```

Compare your model to two others:
1.One using length at birth and gestational age as predictors (main effects only)
2.One using head circumference, length, sex, and all interactions (including the three-way interaction) between these
```{r}
model_fit1 = lm(bwt ~ blength + gaweeks, data = baby_df)
model_fit2 = lm(bwt ~ bhead*blength*babysex, data = baby_df)
summary(model_fit1)
summary(model_fit2)
```

```{r}
anova(model_fit1, bweight_lm) %>% 
  broom::tidy()
```

Make this comparison in terms of the cross-validated prediction error; use crossv_mc and functions in purrr as appropriate.
```{r}

```


```{r}
baby_df %>% 
  modelr::add_residuals(model_fit) %>% 
  ggplot(aes(x = gaweeks, y = resid)) + 
  geom_point()
```

# Problem 3
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

